NFL Draft Analysis

### 2020-05-11 draft_analysis.Rmd
Add testing for ML model

```{r scraping}

@@

```{r scrape2020}

@@

Next we will scrape the AP Offensive Rookie of the Year Winners from the same website.

@@

@@

@@

Now let's use the model to predict the probabilities that each player from the 2020 draft will become Offensive Rookie of the Year.  This code will give us the probability that the model is sure about its choice that the observation will fall under the "No" and "Yes" category.

```{r eval}

predictions <- predict(object=model, df_2020[,predictor_names], type='prob')
kable(head(predictions))
```

@@

df_2020 <- merge(df_2020, predictions, by = "row.names", all.x = FALSE, all.y = FALSE)
df_2020$No.x <- NULL
```

>>>>

```{r scrape_master}

@@

```{r scrape_2020}

@@

We will also scrape the 2017-2019 NFL draft data into a seperate dataframe *test_df*, which will be used to test our machine learning model that we will develop later in the tutorial.

```{r scrape_test}
test_df <- data.frame()
for (year in 2017:2019){

  # get rid of the columns we dont care about
  df <- df[,1:6]

  test_df <- rbind(test_df, df)
}

Next we will scrape the AP Offensive Rookie of the Year Winners from the same website, again for our machine learning problem.

@@

We will process the *test_df* dataframe in the same way.

```{r process_test}

# filter out certain rounds
test_df <- test_df %>%
  filter(Rnd < 8)

# get rid of blank rows
test_df <-test_df[!(test_df$Player=="Player"),]

# filter so dataframe only contains offensive skill position players.
test_df <- test_df %>%
  filter(Pos == "QB" | Pos == "WR" | Pos == "RB")

test_df[is.na(test_df)] <- 22

test_df$Pick <- as.integer(test_df$Pick)
test_df$Age <- as.integer(test_df$Age)
test_df$Tm <- as.factor(test_df$Tm)
test_df$Pos <- as.factor(test_df$Pos)

kable(head(test_df))
```

@@

Let's test our model against the 2017, 2018, and 2019 datasets. To do this, we will use the *predict()* function in the caret package and feed it the test data. From there,  *predict()* will calculate probabilities that the model is sure about it choice that each observation from *test_df* will fall under the "Yes" and "No" outcome categories. So the "Yes" variable corresponds to the probability the model is sure about its choice that the player will become Rookie MVP, and "No" = probability the model is sure the player will not be the Rookie MVP.

```{r eval_test}

predictions <- predict(object=model, test_df[,predictor_names], type='prob')
kable(head(predictions))
```

```{r join_probabilities_test}

test_df <- merge(test_df, predictions, by = "row.names", all.x = FALSE, all.y = FALSE)
test_df$No.x <- NULL

kable(head(test_df))
```

Now let's get the top 10 players that the model is most certain will be the Offensive Rookie of the Year for 2017, 2018, and 2019.

```{r top10_roty_test}

top10_roty_2017 <- test_df %>%
  filter(year == 2017) %>%
  top_n(10, Yes)

kable(top10_roty_2017)

top10_roty_2018 <- test_df %>%
  filter(year == 2018) %>%
  top_n(10, Yes)

kable(top10_roty_2018)

top10_roty_2019 <- test_df %>%
  filter(year == 2019) %>%
  top_n(10, Yes)

kable(top10_roty_2019)
```

The actual winners for Rookie Offensive MVP for 2017-2019 were Alvin Kamara, Saquon Barkley, and Kyler Murray (in that order). The model fails to list Kamara as a top 10 prediction for 2017, but lists Barkley as its fourth best prediction for 2018, and Murray as its top prediction for 2019!

@@

Now let's use the model to predict the probabilities that each player from the 2020 draft will become Offensive Rookie of the Year.  Like we did for the testing portion, this code will give us the probability that the model is sure about its choice that the observation will fall under the "No" and "Yes" category.

```{r eval_2020}

predictions <- predict(object=model, df_2020[,predictor_names], type='prob')
```

Now let's join our prediction probabilities to the actual data like we did before. s

@@

df_2020 <- merge(df_2020, predictions, by = "row.names", all.x = FALSE, all.y = FALSE)
df_2020$No.x <- NULL
